SIR Model With Testing Flows and Isolation

### 2020-10-21 codes/ali_test_sir.Rmd
P_i changed to 1

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=1,gamma=1/3, omega=0.25, t=0.01, 
             W_s=0.01, W_i=1, W_r=0.01, #weights
             P_s=0, P_i=0.5, P_r=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2 #eta_w/eta_t
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
# Disease free equilibrium
Sn_dfe <-function(params){
  unpack(as.list(params))
  return((t*(1-P_s)*N0)/omega)
}
Su_dfe<- params[["N0"]]-Sn_dfe(params)

>>>>

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=1,gamma=1/3, omega=0.25, t=0.01, 
             W_s=0.01, W_i=1, W_r=0.01, #weights
             P_s=0, P_i=1, P_r=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2 #eta_w/eta_t
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
# Disease free equilibrium
Sn_dfe <-function(params){
  unpack(as.list(params))
  return((t*(1-P_s)*N0)/omega)
}
Su_dfe<- params[["N0"]]-Sn_dfe(params)
